Abstract Binding Trees

### 2015-11-07 paper.tex
[paper] fix typo

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $\mathbf{C}\Grothendieck{}{\Psi}$ represents
  the category of elements of a copresheaf $\Of{\Psi}{\mathbf{C}\to\Sets}$ but
  we keep the $\mathbf{C}$ implicit and simply refer to it as the Grothendieck
  construction. Alternatively, this construction can be understood as a coend
  $\IMode{\mathbf{C}\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in
      \mathbf{C}}\Coslice{c}{\mathbf{C}} \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{\mathbf{C}}\to\Cats}$ on operators, we have a
category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$ for
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\FLift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the the codomain Grothendieck bifibration $\pi_{cod}$ where
$\pi_{\Operators}$ is also a discrete Grothendieck opfibration:

>>>>

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $\mathbf{C}\Grothendieck{}{\Psi}$ represents
  the category of elements of a copresheaf $\Of{\Psi}{\mathbf{C}\to\Sets}$ but
  we keep the $\mathbf{C}$ implicit and simply refer to it as the Grothendieck
  construction. Alternatively, this construction can be understood as a coend
  $\IMode{\mathbf{C}\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in
      \mathbf{C}}\Coslice{c}{\mathbf{C}} \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{\mathbf{C}}\to\Cats}$ on operators, we have a
category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$ for
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\FLift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the codomain Grothendieck bifibration $\pi_{cod}$ where
$\pi_{\Operators}$ is also a discrete Grothendieck opfibration:
